### 2019-10-16 README.Rmd
added doi and updated title

# Explore and Evaluate the Mechanisms for Missing Data in the Enhanced Tuberculosis Surveillance System

[![badge](https://img.shields.io/badge/Launch-Analysis-lightblue.svg)](https://mybinder.org/v2/gh/seabbs/ETSMissing/master?urlpath=rstudio)
[![Documentation](https://img.shields.io/badge/Documentation-click here!-lightgrey.svg?style=flat)](https://www.samabbott.co.uk/ETSMissing)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2635687.svg)](https://doi.org/10.5281/zenodo.2635687)

>>>>

# Evaluating the Mechanisms for Missing Data in the Enhanced Tuberculosis Surveillance System

[![badge](https://img.shields.io/badge/Launch-Analysis-lightblue.svg)](https://mybinder.org/v2/gh/seabbs/ETSMissing/master?urlpath=rstudio)
[![Documentation](https://img.shields.io/badge/Documentation-click here!-lightgrey.svg?style=flat)](https://www.samabbott.co.uk/ETSMissing)
[![DOI](https://zenodo.org/badge/214470301.svg)](https://zenodo.org/badge/latestdoi/214470301)
